Assessing Power of the California Microhap Baseline for PBT and relationship inference

### 2025-03-26 003-ckmr-sim-evaluation.Rmd
Notebooks all rendering.
Fix threads iun 003

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf",
    frh_comp = "results/ckmr-sim-eval/frh-comp-figure.pdf",
    frh_comp_crop = "results/ckmr-sim-eval/frh-comp-figure-crop.pdf",
    frh_comp_tex = "tex/images/frh-comp-figure-crop.pdf"

  )
}

@@

@@

```{r}
set.seed(5)
tmp_list <- mclapply(
  X = ckmr_sim_nests$data, 
  FUN = function(x) get_FPRs_and_FNRs(x),
  mc.cores = 8
)

@@

Qsims <- mclapply(input_tibbles$data, get_logl_rats, mc.cores = 8)

@@

# So, instead I just print the thing in the Rstudio window and export it
# at size 13" high by 10" wide. Then I moved it to where it belongs in the tex directory.
asg
```

@@

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
  threads <- as.numeric(snakemake@threads)
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    frh_comp_tex = "tex/images/frh-comp-figure-crop.pdf"
  )
  threads <- 8
}

# add the intermediates that are not really outputs
output_list <- c(
  output_list,
  ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
  ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
  ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
  ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
  frh_comp = "results/ckmr-sim-eval/frh-comp-figure.pdf",
  frh_comp_crop = "results/ckmr-sim-eval/frh-comp-figure-crop.pdf",
  ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf" # ggsave doesn't save this, so see code comments below
)

@@

# ensure that Mendel is installed into the CKMRsim package tree:
install_mendel(Dir = system.file(package = "CKMRsim"))

@@

```{r}
set.seed(5)
tmp_list <- mclapply(
  X = ckmr_sim_nests$data, 
  FUN = function(x) get_FPRs_and_FNRs(x),
  mc.cores = threads
)

@@

Qsims <- mclapply(input_tibbles$data, get_logl_rats, mc.cores = threads)

@@

# So, instead I just print the thing in the Rstudio window and export it
# at size 13" high by 10" wide. Then I moved it to where it belongs in the tex directory.
# at tex/images/cmkr-comp-figure-crop.pdf
asg
```

@@

g8
